Word learning at the semantics pragmatics interface

### 2020-04-20 paper/supplementary_material.Rmd
minor edits

The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

We consider a model that ignores common ground information, $\rho_i$. This model takes in object specific semantic knowledge and speaker informativeness butuses a prior distribution over objects that is constant across alignment conditions and uniform (e.g., [0.5, 0.5]). This model corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation. As a consequence, the listener does not differentiate between the two common ground alignment conditions.

>>>>

The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar vs. unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete ignorance, corresponding to maximal uncertainty about which object the word applies to. 
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

We consider a model that ignores common ground information, $\rho_i$. This model takes in object specific semantic knowledge and speaker informativeness but uses a prior distribution over objects that is constant across alignment conditions and uniform (e.g., [0.5, 0.5]). This model corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation. As a consequence, the listener does not differentiate between the two common ground alignment conditions.
